Kyoto VR MQP Paper First Draft

### 2019-09-25 paper.tex
start deploying editour section

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine. Therefore, we decided to take the time to explore
this framework since it appeared to be more tailored to our specific use case.
Viro Media also recognizes that all developers who wish to create an app with
3D capabilities are not necessarily game developers. Viro Media pitches Viro
AR as ``The perfect alternative to specialized game engines, ViroAR is a
platform for rapidly building ARKit and ARCore apps. Our platform allows
developers to focus on what they do best by leveraging familiar tools and
frameworks used in mobile application development''~\autocite{viro2019}.
While the majority of our team has decent experience with writing Javascript,
we all either have very little or no experience writing React apps.

@@

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to editour'' card provides these instructions, which should be
enough to get started.  A user can only terminate the polygon after two points
have been placed to prevent the user from drawing a region with an area of
zero. Once a region is created, a region card appears in the side bar. From
here, the user can edit anything about the region. From here, the user can edit
anything about the region.

@@

@@

\subsubsection{Adobe XD Design}
\label{sec:adobeXdDesign}
On September 10th, Atticus Sims presented us with a storyboard for the app
experience. We would not be able to resume work until September 17th due to
prior travel plans. Whether Atticus knew this or not, the design he put forth
had ramifications that rippled throughout the entire software stack we had
constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.

@@

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accomodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
is also a text area to include a transcript of the uploaded audio file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption[Additions to the editour to accommodate the new design]
    {Additions to the editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

At this point, the codebase for Editour was already around three thousand lines
of vanilla Javascript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience..
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and... voila!''
We suspect this sounds too good to be true because it is. As of September 20th,
2019, there are 6 user reviews. All of the five-star reviews were have the
caveat ``Reviewer was gifted package by publisher'' which which we interpreted
as a warning sign. Because of this, we decided to rebuild the UI largely from
the ground up, using the Adobe XD file to guide us.

@@

Our first day of on-site testing with the app took place on September 6th.
Using Editour, we rebuilt the izi.TRAVEL audio tour that Atticus already
created. The first version of the rebuilt tour had regions that were relatively
small; some regions were only a few meters across. This version of the tour can
be seen in Figure~\ref{fig:kinkakujiTour}.

>>>>

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine. Therefore, we decided to take the time to explore
this framework since it appeared to be more tailored to our specific use case.
Viro Media also recognizes that all developers who wish to create an app with
3D capabilities are not necessarily game developers. Viro Media pitches Viro
AR as ``The perfect alternative to specialized game engines, ViroAR is a
platform for rapidly building ARKit and ARCore apps. Our platform allows
developers to focus on what they do best by leveraging familiar tools and
frameworks used in mobile application development''~\autocite{viro2019}.
While the majority of our team has decent experience with writing JavaScript,
we all either have very little or no experience writing React apps.

@@

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to Editour'' card provides these instructions, which should be
enough to get started.  A user can only terminate the polygon after two points
have been placed to prevent the user from drawing a region with an area of
zero. Once a region is created, a region card appears in the side bar. From
here, the user can edit anything about the region. From here, the user can edit
anything about the region.

@@

\subsubsection{Deploying the Editour Backend}
\label{sec:deployingTheEditourBackend}

For testing and development purposes the Editour backend was originally hosted
on a personal server belonging to a member of our team. This was a CentOS
virtual machine running on an old Dell rack server in Worcester, Massachusetts.
We wrote a custom systemd service to run the Editour as a daemon and keep its
log files organized. The Node.js backend was served by an Nginx reverse proxy
running on the same virtual machine.

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and
shared hosting environment for us to use on September 23\textsuperscript{rd}.
Unfortunately, this shared hosting environment was designed for running simple
PHP applications like WordPress, so it took a bit of work to coerce it into
running a Node.js application.

@@

\subsubsection{Adobe XD Design}
\label{sec:adobeXdDesign}

On September 10\textsuperscript{th} Atticus Sims presented us with a storyboard
for the app experience. We would not be able to resume work until September
17\textsuperscript{th} due to prior travel plans. Whether Atticus knew this or
not, the design he put forth had ramifications that rippled throughout the
entire software stack we had constructed up to this point.
Figure~\ref{fig:adobeXdDesign} shows this design.

@@

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accommodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
is also a text area to include a transcript of the uploaded audio file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption[Additions to the Editour to accommodate the new design]
    {Additions to the Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience..
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and... voila!''
We suspect this sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.

@@

Our first day of on-site testing with the app took place on September
6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
Atticus already created. The first version of the rebuilt tour had regions that
were relatively small; some regions were only a few meters across. This version
of the tour can be seen in Figure~\ref{fig:kinkakujiTour}.
